### 2018-04-13 linearity-2018/dialectica-spaces.tex
Adding a link to the Agda formalization.

Dialectica categories were first introduced by de Paiva as a
categorification of G\"odel's Dialectica interpretation
\cite{depaiva1990}.  Dialectica categories were one of the first sound
categorical models of intuitionistic linear logic with linear
modalities.  We show in this section that they can be adapted to
become a sound and complete model for CNC logic, with both the
exchange and of-course modalities.  Due to the complexities of working
with dialectica categories we have formally verified\footnote{The
  complete formalization can be found online at \url{}.}  this
section in the proof assistant Agda~\cite{bove2009}.

>>>>

Dialectica categories were first introduced by de Paiva as a
categorification of G\"odel's Dialectica interpretation
\cite{depaiva1990}.  Dialectica categories were one of the first sound
categorical models of intuitionistic linear logic with linear
modalities.  We show in this section that they can be adapted to
become a sound and complete model for CNC logic, with both the
exchange and of-course modalities.  Due to the complexities of working
with dialectica categories we have formally verified\footnote{The
  complete formalization can be found online at
  \url{https://github.com/MonoidalAttackTrees/non-comm-monads-adjoint-models/tree/master/dialectica-formalization}.}
this section in the proof assistant Agda~\cite{bove2009}.
